---
title: "Time Series Comparison"
author: "Tanmoy Das - 2248117"
date: '2023-01-14'
output: word_document
---

# Title
Comparison of different methods for forecasting stock market

# Installing necessaary packages
```{r}
library(readr)
library(ggplot2)
library(forecast)
library(fpp2)
library(TTR)
library(dplyr)
library(xts)
library(tidyverse)
library(quantmod)
library(tseries)
library(rugarch)
library(prophet)
library(tsfknn)
```

# Reading the data
```{r}
rawdata = read.csv("C:/Users/TANMOY/Desktop/Datasets/Mastercard_stock_history.csv", header = TRUE, row.names = "Date")
glimpse(rawdata)
tail(index(rawdata))
chartSeries(rawdata)
```

# Splitting the data
```{r}
N = length (rawdata$Close)
n = 0.8*N

train = rawdata$Close[1:n]
test = rawdata$Close[(n+1):N]
```

# ARIMA Model
## Augmented Dickey-Fuller test for checking stationarity
```{r}
print(adf.test(train))
```

## ACF & PACF for the train data
```{r}
par(mfrow = c(1,2))
acf(train)
pacf(train)
par(mfrow=c(1,1))
```
# Decomposition
```{r}
train.ts = ts(train, start = c(2006,5), end = c(2021,10), frequency = 3)
plot(decompose(train.ts))
```


# Fitting the model

```{r}
modelfit = auto.arima(train, lambda = "auto")
summary(modelfit)
```
## Diagonistics on residuals
```{r}
plot(resid(modelfit),ylab="Residuals",main="Residuals(Arima(1,1,1)) vs. Time")


# Histogram of Residuals & Normality Assumption
hist(resid(modelfit),freq=F,ylim=c(0,10),main="Histogram of Residuals")
e=resid(modelfit)
curve(dnorm(x, mean=mean(e), sd=sd(e)), add=TRUE, col="red")
box()

tsdiag(modelfit)

Box.test(modelfit$residuals, lag= 2, type="Ljung-Box")
Box.test(modelfit$residuals, type="Ljung-Box")
```
## Plotting the model
```{r}
plot(as.ts(train))
lines(modelfit$fitted,col="red")
```

# Predicting the close values for test data and plotting them
```{r}
predlen= length(test)
trainarima_fit <- forecast(modelfit, h= predlen)

plot(trainarima_fit)
head(trainarima_fit$mean)
```
# Plotting mean predicted  values vs real data
```{r}
meanvalues<- as.vector(trainarima_fit$mean)
precios <- as.vector(test)
plot(meanvalues, type = "l",col="red")
lines(precios, type = "l")
```